How many researchers use 'boilerplate' statistical analysis sections?

### 2021-03-12 manuscript/draft_manuscript.Rmd
update draft manuscript

```{r}
load('wordcount.plos.rda')
n.words = wordcounts %>% summarise(med = median(words),q1=quantile(words,.25),q3=quantile(words,.75))
```

@@

The median length of statistical methods sections after text cleaning was `r n.words[['med']]` per DOI (IQR: `r n.words[['q1']]` to `r n.words[['q3']]`) (Figure 1B).

Across all records included in analysis, all included Biology and life sciences (n = `r n.biology`), Earth sciences
(n = `r n.earth`) and/or Computer and information sciences (n = `r n.computer`) within their top 3 subject classifications
(Figure 1C).

>>>>

```{r}
load('wordcount.plos.rda')
n.words = wordcounts %>% summarise(med = median(words),q1=quantile(words,.25),q3=quantile(words,.75))
p.extremes = wordcounts %>% summarise(morethan500 = round(100*mean(words>500)),lessthan50=round(100*mean(words<50)))

@@

The median length of statistical methods sections was `r n.words[['med']]` words (IQR: `r n.words[['q1']]` to `r n.words[['q3']]` words) (Figure 1B). `r n.extremes[['morethan500']]` articles (`r p.extremes[['morethan500']]`%) had a statistical methods section of 500 words or more. `r n.extremes[['lessthan50']]` articles (`r p.extremes[['lessthan50']]`%) had a statistical methods section of 50 words or less, equal to the length of this paragraph.

All papers included Biology and life sciences (n = `r n.biology`), Earth sciences
(n = `r n.earth`) and/or Computer and information sciences (n = `r n.computer`) within their top 3 subject classifications
(Figure 1C).

```{r,fig.width=10,fig.cap="\\label{fig:plot-5-topics}}

include_graphics{'figures/plosone.5topics.jpg'}

```{r,fig.width=10,fig.cap="\\label{fig:plot-10-topics}}

include_graphics{'figures/plosone.10topics.jpg'}
